---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LAPS

The `LAPS` package for R bundles the data
collected in the
[LAPS](http://www.centre-multilingualism.ch/en/content/language-aptitude-why-and-how-assess-it)
(Institute of Multilingualism, Fribourg, Switzerland).

## Installation

You can install the `LAPS` package as follows. (Make sure the `devtools` package
is installed.)

```r
library(devtools)
install_github("janhove/LAPS")
```

## Datasets

Two datasets are included:

* `construct_scores`: Construct scores for the cognitive and questionnaire-based constructs.
* `full_data`: All data.

To make these datasets available in your `R` session:

```{r}
library(LAPS)
data(construct_scores)
dim(construct_scores)
data(full_data)
dim(full_data)
```


For more information about these datasets, see the technical report
at https://osf.io/hstv7/.

## Reference

If you use these datasets, please cite it appropriately:

  Jan Vanhove, Raphael Berthele, Carina Steiner, Hansjakob Schneider and
  Isabelle Udry (2020). LAPS: Datasets for the 'Language Aptitude: Why and How
  to Assess it?' Project. R package version 1.0.0.
  https://github.com/janhove/LAPS
